---
title: "Cereals"
author: "Sameer"
date: "March 7, 2018"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

#              #######---  PROJECT I - CEREALS  ---#######
# Scope of the Project - EDA (Exploratory Data Analysis)

# Introduction to EDA (Exploratory Data Analysis)---
# EDA is a data analysis approach. There are totally three popular data analysis 
# approaches as enlisted below:---

# a) Classical
# b) Exploratory (EDA)
# c) Bayesian

# Paradigms for Analysis techniques---
# These three approaches are similar in that they all start with a 
# general science/engineering problem and all yield science/engineering # conclusions. The difference is the sequence and focus of the 
# intermediate steps. 
  
# a) For classical analysis, the sequence is---
# Problem => Data => Model => Analysis => Conclusions 

# b) For EDA, the sequence is---
# Problem => Data => Analysis => Model => Conclusions 

# c) For Bayesian, the sequence is---
# Problem => Data => Model => Prior Distribution => Analysis => 
# Conclusions

# Salient features of EDA (Exploratory Data Analysis)---
# i) Model - The Exploratory Data Analysis approach does not impose 
# deterministic or probabilistic models on the data. On the contrary,
# the EDA approach allows the data to suggest admissible models that 
# best fit the data. 

# ii) Focus - For exploratory data analysis (EDA), the focus is on the # data--its structure, outliers, and models suggested by the data. 

# iii) Techniques - EDA techniques are generally graphical. They 
# include scatter plots, character plots, box plots, histograms, bihistograms, probability plots, residual plots, and mean plots. 

# iv) Rigor - EDA techniques do not share in that rigor or formality. 
# EDA techniques make up for that lack of rigor by being very 
# suggestive, indicative, and insightful about what the appropriate 
# model should be.

# EDA techniques are subjective and depend on interpretation which may 
# differ from analyst to analyst, although experienced analysts 
# commonly arrive at identical conclusions. 

# v) Data Treatment - The EDA approach, on the other hand, often makes 
# use of (and shows) all of the available data. In this sense there is 
# no corresponding loss of information. 

# vi) Many EDA techniques make little or no assumptions--they present 
# and show the data--all of the data--as is, with fewer encumbering
# assumptions. 

# vii)Applications of EDA (Exploratory Data Analysis)---
# a) EDA has as its broadest goal the desire to gain insight into the 
# engineering/scientific process behind the data.
# b) EDA is active and futuristic. 

# viii) Goals of EDA (Exploratory Data Analysis)---
# The primary goal of EDA is to maximize the analyst's insight into a 
# dataset and into the underlying structure of a data set, while 
# providing all of the specific items that an analyst would want to 
# extract from a data set, such as:

# 1) a good-fitting, parsimonious model
# 2) a list of outliers
# 3) a sense of robustness of conclusions
# 4) estimates for parameters
# 5) uncertainties for those estimates
# 6) a ranked list of important factors
# 7) conclusions as to whether individual factors are statistically 
#    significant
# 8) optimal settings

# iX) Data Insights - Insight implies detecting and uncovering 
# underlying structure 
# in the data. Such underlying structure may not be encapsulated in the
# list of items above; such items serve as the specific targets of an 
# analysis, The "feel" for the data comes almost exclusively from the
# application of various graphical techniques, the collection of which
# serves as the window into the essence of the data. Graphics are
# irreplaceable--there are no quantitative analogues that will give the
# same insight as well-chosen graphics.

# Statistics and data analysis procedures can broadly be split into two 
# parts:
  # 1) Quantitative
  # 2) Graphical 

# 1) Quantitative -	Quantitative techniques are the set of statistical 
# procedures that yield numeric or tabular output. Examples of quantitative 
# techniques include:
  
# a) Hypothesis testing
# b) Analysis of variance
# c) Point estimates and confidence intervals
# d) Least squares regression 

# These and similar techniques are all valuable and are mainstream in
# terms of classical analysis. 

# 2) Graphical - On the other hand, there is a large collection of
# statistical tools that we generally refer to as graphical techniques. 
# These include:
  
# a) Scatter plots
# b) Histograms
# c) Probability plots
# d) Residual plots
# e) Box plots
# f) Block plots 

# EDA Approach Relies Heavily on Graphical Techniques--- 	
# The EDA approach relies heavily on these and similar graphical 
# techniques. 
# Such graphical tools are the shortest path to gaining insight into a
# dataset in terms of the following---

# a) testing assumptions
# b) model selection
# c) model validation
# d) estimator selection
# e) relationship identification
# f) factor effect determination
# g) outlier detection 

# If one is not using statistical graphics, then one is forfeiting
# insights into one or more aspects of the underlying structure of the # data.

```{r cars, echo = TRUE}

```

```{r pressure}
plot(pressure)
```
## Global R Codes---
```{r}
(package="datasets")
# to prevent strings or characters being converted to Factors
options(stringsAsFactors=FALSE)
# to prevent conversion of mathematical values to scientific/exponential values
options(scipen=999)
```
# Importing & Execution of the packages in R environment---
```{r}
library(varhandle)
library(magrittr)
library(googlesheets)
library(gsheet)
library(data.table)
library(googleVis)
library(knitr)
library(summarytools)
library(descr)
library(gmodels)
library(Deducer)
library(plyr)
library(agricolae)
library(prettyR)
library(reporttools)
library(stringi)
library(corrplot)
library(gclus)
library(caTools)
library(Hmisc)
library(e1071)
library(lmtest)
library(car)
library(MASS)
library(ggpubr)
library(caret)
library(DAAG)
library(Metrics)
library(usdm)
library(dplyr)
library(sqldf)
library(graphics)
library(ggplot2)
library(mlbench)
library(multcomp)
library(utils)
library(rcompanion)
library(scales)
library(nortest)
library(RcmdrMisc)
```
# Importing the dataset into R environment---
```{r}
Cereals<-read.csv("C://Users/User/Documents/R/R Projects/Cereals.csv",  header = TRUE, sep=",", stringsAsFactors=FALSE)
View(Cereals)

Cereals<-read.csv("E://Back up 1/ACADGILD/Dr Vinod/Project I - Cereals_practice.csv", header = TRUE, sep=",", stringsAsFactors=FALSE)
View(Cereals)

setwd("C://Users/User/Documents/R/R Projects")
install.packages("xlsx")
library(xlsx)
require(xlsx)
require(ggplot2)

setwd("E://Back up 1/ACADGILD/DrVinod")
Cereals<-read.xlsx("Cereals_practice.xlsx",sheetIndex = 1)
View(Cereals)
```
# Know your data---
```{r}
names(Cereals) # Lists the names of the variables in the given dataset
nrow(Cereals) # To find the Number of rows 
ncol(Cereals) # To find the number of Columns
dim(Cereals) # To display the dimensions of the given table (i.e. Rows 
# and Columns) at a glance
str(Cereals) # To list the structure of the given Dataset
class(Cereals) # To find the structure of the given dataset using R 
# tool
attributes(Cereals) # To find the Row Names, Column Names and the given 
# dataset structure
```
# To check for the Missing Values & their Identification---
```{r}
colSums(is.na(Cereals))
# OR---
sapply(Cereals, function(y) sum(is.na(y)))
# OR---
sum(complete.cases(Cereals))
sum(!complete.cases(Cereals))
# OR ---
sum(is.na(Cereals$name))
sum(is.na(Cereals$mfr))
sum(is.na(Cereals$type))
sum(is.na(Cereals$calories))
sum(is.na(Cereals$protein))
sum(is.na(Cereals$sodium))
sum(is.na(Cereals$fiber))
sum(is.na(Cereals$carbo)) # 1 missing value
sum(is.na(Cereals$sugars)) # 1 missing value
sum(is.na(Cereals$potass)) # 2 missing values
sum(is.na(Cereals$vitamins))
sum(is.na(Cereals$shelf))
sum(is.na(Cereals$weight))
sum(is.na(Cereals$cups))
sum(is.na(Cereals$rating))

# To check for Row-Numbers with NA specified/Missing values---
unique (unlist (lapply (Cereals, function (x) which (is.na (x)))))
which(is.na(Cereals), arr.ind=TRUE)

# Checking for % of missing value columnwise--- 
round(colSums(is.na(Cereals))/nrow(Cereals),4)*100

# OR---

# To check for  % of missing value  in the overall dataset---
# a) To check for Total Number of records 
nRows = nrow(Cereals)
# b) Total Number of records without any missing values 
nComplete = sum(complete.cases(Cereals))
nComplete
# c) Calculation regarding the % of Loss of Data in case if the missing values # are deleted
dataLoss = (1- nComplete/nRows)*100 
dataLoss

# Check missing data pattern & Visualization-----
library(mice)
md.pattern(Cereals)

# Visulize the missing data pattern--- 
library(VIM)

aggr(Cereals)

mice_plot <- aggr(Cereals[,c("carbo","sugars","potass")],   
                  col=c('darkgreen','yellow'),
                  numbers=TRUE, sortVars=TRUE,
                  labels=c("Carbo","Sugars","Potassium"),                   cex.axis=.7,gap=3, ylab=c("Missing data","Pattern"))
```
# To deal with the Missing Values/Treatment of Missing values 
# by using Mean-Imputation Method---
```{r}
library(Hmisc)
# carbo<-round(impute(Cereals$carbo, mean),1)
# sugars<-round(impute(Cereals$sugars,mean),1)
# potass<-round(impute(Cereals$potass,mean),1)

# carbo
# sugars
# potass

#Replacement of the Missing values with the Mean Imputation Method---

Cereals$carbo<- round(ifelse(is.na(Cereals$carbo), mean(Cereals$carbo, na.rm=TRUE), Cereals$carbo),1)
Cereals$carbo
Cereals$sugars<- round(ifelse(is.na(Cereals$sugars), mean(Cereals$sugars, na.rm=TRUE), Cereals$sugars),1)
Cereals$sugars
Cereals$potass<- round(ifelse(is.na(Cereals$potass), mean(Cereals$potass, na.rm=TRUE), Cereals$potass),1)
Cereals$potass

# transform(Cereals, y = ifelse(is.na(carbo), mean(carbo, na.rm=TRUE), y))
#is.na(Cereals$carbo) 

View(Cereals)

```
# To find Outliers in the dataset---
```{r}
library(outliers)

#Only select those columns having Numeric values---
cereal_val<-Cereals[, 4:16]
View(cereal_val)

# Or ----

cereal_val <- sapply(Cereals, is.numeric)
cereal_val <- Cereals[,cereal_val]
View(cereal_val)


# Detection of Outliers---
# a) Identification of Outliers and corresponding row-numbers---
outlier_tf=outlier(Cereals$calories,logical=TRUE)
outlier_tf
find_outlier = which(outlier_tf==TRUE,arr.ind=TRUE)
find_outlier

outlier_tf=outlier(Cereals$protein,logical=TRUE)
outlier_tf
find_outlier = which(outlier_tf==TRUE,arr.ind=TRUE)
find_outlier

outlier_tf=outlier(Cereals$fat,logical=TRUE)
outlier_tf
find_outlier = which(outlier_tf==TRUE,arr.ind=TRUE)
find_outlier

outlier_tf=outlier(Cereals$sodium,logical=TRUE)
outlier_tf
find_outlier = which(outlier_tf==TRUE,arr.ind=TRUE)
find_outlier

outlier_tf=outlier(Cereals$fiber,logical=TRUE)
outlier_tf
find_outlier = which(outlier_tf==TRUE,arr.ind=TRUE)
find_outlier

outlier_tf=outlier(Cereals$carbo,logical=TRUE)
outlier_tf
find_outlier = which(outlier_tf==TRUE,arr.ind=TRUE)
find_outlier

outlier_tf=outlier(Cereals$sugars,logical=TRUE)
outlier_tf
find_outlier = which(outlier_tf==TRUE,arr.ind=TRUE)
find_outlier

outlier_tf=outlier(Cereals$potass,logical=TRUE)
outlier_tf
find_outlier = which(outlier_tf==TRUE,arr.ind=TRUE)
find_outlier

outlier_tf=outlier(Cereals$vitamins,logical=TRUE)
outlier_tf
find_outlier = which(outlier_tf==TRUE,arr.ind=TRUE)
find_outlier

outlier_tf=outlier(Cereals$shelf,logical=TRUE)
outlier_tf
find_outlier = which(outlier_tf==TRUE,arr.ind=TRUE)
find_outlier

outlier_tf=outlier(Cereals$weight,logical=TRUE)
outlier_tf
find_outlier = which(outlier_tf==TRUE,arr.ind=TRUE)
find_outlier

outlier_tf=outlier(Cereals$cups,logical=TRUE)
outlier_tf
find_outlier = which(outlier_tf==TRUE,arr.ind=TRUE)
find_outlier

outlier_tf=outlier(Cereals$rating,logical=TRUE)
outlier_tf
find_outlier = which(outlier_tf==TRUE,arr.ind=TRUE)
find_outlier


# b) Using lofactor() under package DMwR

library(DMwR)
outlier.scores.lof <- lofactor(cereal_val, k=5)
outlier.scores.lof

outliers_detect<-print(cereal_val[which(outlier.scores.lof > 1.5), ])
outliers_detect

# c) Creating a function to detect outliers via Boxplot---
box <- function(df){
  #outlier detection using boxplot
  outliers <- c()
  for(i in 1:ncol(df)){
    box <- boxplot(df[,i])
    for(j in 1:length(box$out)){
      a = which(df[,i] == box$out[j])
      if(length(a) == 1){
        outliers[length(outliers) + 1] <- a 
      }
    }
  }
  return(unique(outliers))
  #outliers
}

box(cereal_val)

# c) User defined script---
source("http://goo.gl/UUyEzD")
outlierKD(Cereals, calories)
outlierKD(Cereals, protein)
outlierKD(Cereals, fat)
outlierKD(Cereals, sodium)
outlierKD(Cereals, fiber)
outlierKD(Cereals, carbo)
outlierKD(Cereals, sugars)
outlierKD(Cereals, potass)
outlierKD(Cereals, vitamins)
outlierKD(Cereals, shelf)
outlierKD(Cereals, weight)
outlierKD(Cereals, cups)
outlierKD(Cereals, rating)
```
# Treatment of Outliers---
```{r}
# a) User-defined function for Scoping of Outliers---
fun <- function(x){
  quantiles <- quantile( x, c(.05, .95 ) )
  print(quantiles)
  x[ x < quantiles[1] ] <- quantiles[1]
  x[ x > quantiles[2] ] <- quantiles[2]
  x
}

fun(Cereals$calories)
fun(Cereals$protein)
fun(Cereals$fat)
fun(Cereals$sodium)
fun(Cereals$fiber)
fun(Cereals$carbo)
fun(Cereals$sugars)
fun(Cereals$potass)
fun(Cereals$vitamins)
fun(Cereals$shelf)
fun(Cereals$weight)
fun(Cereals$cups)
fun(Cereals$rating)

# Or ---
# b) Dealing with Outliers/Median Imputation---

cereal_val<-rm.outlier(cereal_val, fill = TRUE, median = TRUE, opposite = FALSE)
cereal_val
View(cereal_val)


qplot(data=Cereals, x=carbo, y=calories)
```
# Descriptive Statistics of the given dataset---
```{r}
# summary() # - it gives the following output--
# i) numeric variables: minimum, maximum, mean, median, and the first (25%) and third (75%) quartiles
# ii) categorical variables (factors): frequency of every level

summary(Cereals)
# OR -----
library(Hmisc)
# describe() - Under Hmisc package, describe() generates the following 
# outcome viz.:
# n, nmiss, unique, mean, 5,10,25,50,75,90,95th percentiles
# 5 lowest and 5 highest scores
describe(Cereals)

library(psych)
# Under psych package,describe() generates the following outcome viz.:
# vars  n   mean  sd median trimmed   mad   min   max  range  skew kurtosis
describe(Cereals)

library(pastecs)
# Under pastecs packgage,stat.desc() generates the following outcome viz.:
# nbr.val, nbr.null, nbr.na, min max, range, sum,
# median, mean, SE.mean, CI.mean, var, std.dev, coef.var
stat.desc(Cereals)

```
# To find n values or Frequencies---
```{r}
table(Cereals$name)
table(Cereals$mfr)
table(Cereals$type)

# To find 2-Way Frequencies/Counts(n)----

table(Cereals$mfr, Cereals$name)
table(Cereals$type, Cereals$name)
table(Cereals$calories, Cereals$name)
table(Cereals$protein, Cereals$name)
table(Cereals$fat, Cereals$name)
table(Cereals$sodium, Cereals$name)
table(Cereals$fiber, Cereals$name)
table(Cereals$carbo, Cereals$name)
table(Cereals$sugars, Cereals$name)
table(Cereals$potass, Cereals$name)
table(Cereals$vitamins, Cereals$name)
table(Cereals$shelf, Cereals$name)
table(Cereals$weight, Cereals$name)
table(Cereals$cups, Cereals$name)
table(Cereals$rating, Cereals$name)


table(Cereals$name, Cereals$mfr)
table(Cereals$mfr, Cereals$mfr)
table(Cereals$type, Cereals$mfr)
table(Cereals$calories, Cereals$mfr)
table(Cereals$protein, Cereals$mfr)
table(Cereals$fat, Cereals$mfr)
table(Cereals$sodium, Cereals$mfr)
table(Cereals$fiber, Cereals$mfr)
table(Cereals$carbo, Cereals$mfr)
table(Cereals$sugars, Cereals$mfr)
table(Cereals$potass, Cereals$mfr)
table(Cereals$vitamins, Cereals$mfr)
table(Cereals$shelf, Cereals$mfr)
table(Cereals$weight, Cereals$mfr)
table(Cereals$cups, Cereals$mfr)
table(Cereals$rating, Cereals$mfr)

table(Cereals$name, Cereals$type)
table(Cereals$mfr, Cereals$type)
table(Cereals$type, Cereals$type)
table(Cereals$calories, Cereals$type)
table(Cereals$protein, Cereals$type)
table(Cereals$fat, Cereals$type)
table(Cereals$sodium, Cereals$type)
table(Cereals$fiber, Cereals$type)
table(Cereals$carbo, Cereals$type)
table(Cereals$sugars, Cereals$type)
table(Cereals$potass, Cereals$type)
table(Cereals$vitamins, Cereals$type)
table(Cereals$shelf, Cereals$type)
table(Cereals$weight, Cereals$type)
table(Cereals$cups, Cereals$type)
table(Cereals$rating, Cereals$type)


table(Cereals$name, Cereals$calories)
table(Cereals$mfr, Cereals$calories)
table(Cereals$type, Cereals$calories)
table(Cereals$calories, Cereals$calories)
table(Cereals$protein, Cereals$calories)
table(Cereals$fat, Cereals$calories)
table(Cereals$sodium, Cereals$calories)
table(Cereals$fiber, Cereals$calories)
table(Cereals$carbo, Cereals$calories)
table(Cereals$sugars, Cereals$calories)
table(Cereals$potass, Cereals$calories)
table(Cereals$vitamins, Cereals$type)
table(Cereals$shelf, Cereals$calories)
table(Cereals$weight, Cereals$calories)
table(Cereals$cups, Cereals$calories)
table(Cereals$rating, Cereals$calories)


table(Cereals$name, Cereals$protein)
table(Cereals$mfr, Cereals$protein)
table(Cereals$type, Cereals$protein)
table(Cereals$calories, Cereals$protein)
table(Cereals$protein, Cereals$protein)
table(Cereals$fat, Cereals$protein)
table(Cereals$sodium, Cereals$protein)
table(Cereals$fiber, Cereals$protein)
table(Cereals$carbo, Cereals$protein)
table(Cereals$sugars, Cereals$protein)
table(Cereals$potass, Cereals$protein)
table(Cereals$vitamins, Cereals$protein)
table(Cereals$shelf, Cereals$protein)
table(Cereals$weight, Cereals$protein)
table(Cereals$cups, Cereals$protein)
table(Cereals$rating, Cereals$protein)

table(Cereals$name, Cereals$fat)
table(Cereals$mfr, Cereals$fat)
table(Cereals$type, Cereals$fat)
table(Cereals$calories, Cereals$fat)
table(Cereals$protein, Cereals$fat)
table(Cereals$fat, Cereals$fat)
table(Cereals$sodium, Cereals$fat)
table(Cereals$fiber, Cereals$fat)
table(Cereals$carbo, Cereals$fat)
table(Cereals$sugars, Cereals$fat)
table(Cereals$potass, Cereals$fat)
table(Cereals$vitamins, Cereals$fat)
table(Cereals$shelf, Cereals$fat)
table(Cereals$weight, Cereals$fat)
table(Cereals$cups, Cereals$fat)
table(Cereals$rating, Cereals$fat)

table(Cereals$name, Cereals$sodium)
table(Cereals$mfr, Cereals$sodium)
table(Cereals$type, Cereals$sodium)
table(Cereals$calories, Cereals$sodium)
table(Cereals$protein, Cereals$sodium)
table(Cereals$fat, Cereals$sodium)
table(Cereals$sodium, Cereals$sodium)
table(Cereals$fiber, Cereals$sodium)
table(Cereals$carbo, Cereals$sodium)
table(Cereals$sugars, Cereals$sodium)
table(Cereals$potass, Cereals$sodium)
table(Cereals$vitamins, Cereals$sodium)
table(Cereals$shelf, Cereals$sodium)
table(Cereals$weight, Cereals$sodium)
table(Cereals$cups, Cereals$sodium)
table(Cereals$rating, Cereals$sodium)

table(Cereals$name, Cereals$fiber)
table(Cereals$mfr, Cereals$fiber)
table(Cereals$type, Cereals$fiber)
table(Cereals$calories, Cereals$fiber)
table(Cereals$protein, Cereals$fiber)
table(Cereals$fat, Cereals$fiber)
table(Cereals$sodium, Cereals$fiber)
table(Cereals$fiber, Cereals$fiber)
table(Cereals$carbo, Cereals$fiber)
table(Cereals$sugars, Cereals$fiber)
table(Cereals$potass, Cereals$fiber)
table(Cereals$vitamins, Cereals$fiber)
table(Cereals$shelf, Cereals$fiber)
table(Cereals$weight, Cereals$fiber)
table(Cereals$cups, Cereals$fiber)
table(Cereals$rating, Cereals$fiber)

table(Cereals$name, Cereals$carbo)
table(Cereals$mfr, Cereals$carbo)
table(Cereals$type, Cereals$carbo)
table(Cereals$calories, Cereals$carbo)
table(Cereals$protein, Cereals$carbo)
table(Cereals$fat, Cereals$carbo)
table(Cereals$sodium, Cereals$carbo)
table(Cereals$fiber, Cereals$carbo)
table(Cereals$carbo, Cereals$carbo)
table(Cereals$sugars, Cereals$carbo)
table(Cereals$potass, Cereals$carbo)
table(Cereals$vitamins, Cereals$carbo)
table(Cereals$shelf, Cereals$carbo)
table(Cereals$weight, Cereals$carbo)
table(Cereals$cups, Cereals$carbo)
table(Cereals$rating, Cereals$carbo)

table(Cereals$name, Cereals$sugars)
table(Cereals$mfr, Cereals$sugars)
table(Cereals$type, Cereals$sugars)
table(Cereals$calories, Cereals$sugars)
table(Cereals$protein, Cereals$sugars)
table(Cereals$fat, Cereals$sugars)
table(Cereals$sodium, Cereals$sugars)
table(Cereals$fiber, Cereals$sugars)
table(Cereals$carbo, Cereals$sugars)
table(Cereals$sugars, Cereals$sugars)
table(Cereals$potass, Cereals$sugars)
table(Cereals$vitamins, Cereals$sugars)
table(Cereals$shelf, Cereals$sugars)
table(Cereals$weight, Cereals$sugars)
table(Cereals$cups, Cereals$sugars)
table(Cereals$rating, Cereals$sugars)

table(Cereals$name, Cereals$potass)
table(Cereals$mfr, Cereals$potass)
table(Cereals$type, Cereals$potass)
table(Cereals$calories, Cereals$potass)
table(Cereals$protein, Cereals$potass)
table(Cereals$fat, Cereals$potass)
table(Cereals$sodium, Cereals$potass)
table(Cereals$fiber, Cereals$potass)
table(Cereals$carbo, Cereals$potass)
table(Cereals$sugars, Cereals$potass)
table(Cereals$potass, Cereals$potass)
table(Cereals$vitamins, Cereals$potass)
table(Cereals$shelf, Cereals$potass)
table(Cereals$weight, Cereals$potass)
table(Cereals$cups, Cereals$potass)
table(Cereals$rating, Cereals$potass)

table(Cereals$name, Cereals$vitamins)
table(Cereals$mfr, Cereals$vitamins)
table(Cereals$type, Cereals$vitamins)
table(Cereals$calories, Cereals$vitamins)
table(Cereals$protein, Cereals$vitamins)
table(Cereals$fat, Cereals$vitamins)
table(Cereals$sodium, Cereals$vitamins)
table(Cereals$fiber, Cereals$vitamins)
table(Cereals$carbo, Cereals$vitamins)
table(Cereals$sugars, Cereals$vitamins)
table(Cereals$potass, Cereals$vitamins)
table(Cereals$vitamins, Cereals$vitamins)
table(Cereals$shelf, Cereals$vitamins)
table(Cereals$weight, Cereals$vitamins)
table(Cereals$cups, Cereals$vitamins)
table(Cereals$rating, Cereals$vitamins)

table(Cereals$name, Cereals$shelf)
table(Cereals$mfr, Cereals$shelf)
table(Cereals$type, Cereals$shelf)
table(Cereals$calories, Cereals$shelf)
table(Cereals$protein, Cereals$shelf)
table(Cereals$fat, Cereals$shelf)
table(Cereals$sodium, Cereals$shelf)
table(Cereals$fiber, Cereals$shelf)
table(Cereals$carbo, Cereals$shelf)
table(Cereals$sugars, Cereals$shelf)
table(Cereals$potass, Cereals$shelf)
table(Cereals$vitamins, Cereals$shelf)
table(Cereals$shelf, Cereals$shelf)
table(Cereals$weight, Cereals$shelf)
table(Cereals$cups, Cereals$shelf)
table(Cereals$rating, Cereals$shelf)

table(Cereals$name, Cereals$weight)
table(Cereals$mfr, Cereals$weight)
table(Cereals$type, Cereals$weight)
table(Cereals$calories, Cereals$weight)
table(Cereals$protein, Cereals$weight)
table(Cereals$fat, Cereals$weight)
table(Cereals$sodium, Cereals$weight)
table(Cereals$fiber, Cereals$weight)
table(Cereals$carbo, Cereals$weight)
table(Cereals$sugars, Cereals$weight)
table(Cereals$potass, Cereals$weight)
table(Cereals$vitamins, Cereals$weight)
table(Cereals$shelf, Cereals$weight)
table(Cereals$weight, Cereals$weight)
table(Cereals$cups, Cereals$weight)
table(Cereals$rating, Cereals$weight)

table(Cereals$name, Cereals$cups)
table(Cereals$mfr, Cereals$cups)
table(Cereals$calories, Cereals$cups)
table(Cereals$protein, Cereals$cups)
table(Cereals$fat, Cereals$cups)
table(Cereals$sodium, Cereals$cups)
table(Cereals$fiber, Cereals$cups)
table(Cereals$carbo, Cereals$cups)
table(Cereals$sugars, Cereals$cups)
table(Cereals$potass, Cereals$cups)
table(Cereals$vitamins, Cereals$cups)
table(Cereals$shelf, Cereals$cups)
table(Cereals$cups, Cereals$cups)
table(Cereals$rating, Cereals$cups)

table(Cereals$name, Cereals$rating)
table(Cereals$mfr, Cereals$rating)
table(Cereals$calories, Cereals$rating)
table(Cereals$protein, Cereals$rating)
table(Cereals$fat, Cereals$rating)
table(Cereals$sodium, Cereals$rating)
table(Cereals$fiber, Cereals$rating)
table(Cereals$carbo, Cereals$rating)
table(Cereals$sugars, Cereals$rating)
table(Cereals$potass, Cereals$rating)
table(Cereals$vitamins, Cereals$rating)
table(Cereals$shelf, Cereals$rating)
table(Cereals$cups, Cereals$rating)
table(Cereals$rating, Cereals$rating)
```
# Other Descriptive Statistics---
# Measures of Central Tendency---
```{r}
# Mean
mean(Cereals$calories)
mean(Cereals$protein)
mean(Cereals$fat)
mean(Cereals$sodium)
mean(Cereals$fiber)
mean(Cereals$carbo)
mean(Cereals$sugars)
mean(Cereals$potass)
mean(Cereals$vitamins)
mean(Cereals$shelf)
mean(Cereals$weight)
mean(Cereals$cups)
mean(Cereals$rating)

# Median---
median(Cereals$calories)
median(Cereals$protein)
median(Cereals$fat)
median(Cereals$sodium)
median(Cereals$fiber)
median(Cereals$carbo)
median(Cereals$sugars)
median(Cereals$potass)
median(Cereals$vitamins)
median(Cereals$shelf)
median(Cereals$weight)
median(Cereals$cups)
median(Cereals$rating)

# Mode---
mode <- function(x) {
  fx <- unique(x)
  fx[which.max(tabulate(match(x, fx)))]
}

mode(Cereals$calories)
mode(Cereals$protein)
mode(Cereals$fat)
mode(Cereals$sodium)
mode(Cereals$fiber)
mode(Cereals$carbo)
mode(Cereals$sugars)
mode(Cereals$potass)
mode(Cereals$vitamins)
mode(Cereals$shelf)
mode(Cereals$weight)
mode(Cereals$cups)
mode(Cereals$rating)

# OR---

# Alternative Code----
mode <- function(x) {
  if (is.numeric(x)) {
    x_vector <- table(x)
    return(as.numeric(names(x_vector)[which.max(x_vector)]))
  }
}

mode(Cereals$calories)
mode(Cereals$protein)
mode(Cereals$fat)
mode(Cereals$sodium)
mode(Cereals$fiber)
mode(Cereals$carbo)
mode(Cereals$sugars)
mode(Cereals$potass)
mode(Cereals$vitamins)
mode(Cereals$shelf)
mode(Cereals$weight)
mode(Cereals$cups)
mode(Cereals$rating)

# Min---
min(Cereals$calories)
min(Cereals$protein)
min(Cereals$fat)
min(Cereals$sodium)
min(Cereals$fiber)
min(Cereals$carbo)
min(Cereals$sugars)
min(Cereals$potass)
min(Cereals$vitamins)
min(Cereals$shelf)
min(Cereals$weight)
min(Cereals$cups)
min(Cereals$rating)

# Max---
max(Cereals$calories)
max(Cereals$protein)
max(Cereals$fat)
max(Cereals$sodium)
max(Cereals$fiber)
max(Cereals$carbo)
max(Cereals$sugars)
max(Cereals$potass)
max(Cereals$vitamins)
max(Cereals$shelf)
max(Cereals$weight)
max(Cereals$cups)
max(Cereals$rating)
```
# Measures of Dispersion---
```{r}
#Range---
range(Cereals$calories)
range(Cereals$protein)
range(Cereals$fat)
range(Cereals$sodium)
range(Cereals$fiber)
range(Cereals$carbo)
range(Cereals$sugars)
range(Cereals$potass)
range(Cereals$vitamins)
range(Cereals$shelf)
range(Cereals$weight)
range(Cereals$cups)
range(Cereals$rating)

# Quartile---
quantile(Cereals$calories)
quantile(Cereals$protein)
quantile(Cereals$fat)
quantile(Cereals$sodium)
quantile(Cereals$fiber)
quantile(Cereals$carbo)
quantile(Cereals$sugars)
quantile(Cereals$potass)
quantile(Cereals$vitamins)
quantile(Cereals$shelf)
quantile(Cereals$weight)
quantile(Cereals$cups)
quantile(Cereals$rating)

# IQR (Inter-Quantile Range)---
IQR(Cereals$calories)
IQR(Cereals$protein)
IQR(Cereals$fat)
IQR(Cereals$sodium)
IQR(Cereals$fiber)
IQR(Cereals$carbo)
IQR(Cereals$sugars)
IQR(Cereals$potass)
IQR(Cereals$vitamins)
IQR(Cereals$shelf)
IQR(Cereals$weight)
IQR(Cereals$cups)
IQR(Cereals$rating)

# Standard Deviation---
sd(Cereals$calories)
sd(Cereals$protein)
sd(Cereals$fat)
sd(Cereals$sodium)
sd(Cereals$fiber)
sd(Cereals$carbo)
sd(Cereals$sugars)
sd(Cereals$potass)
sd(Cereals$vitamins)
sd(Cereals$shelf)
sd(Cereals$weight)
sd(Cereals$cups)
sd(Cereals$rating)

# Variance---
var(Cereals$calories)
var(Cereals$protein)
var(Cereals$fat)
var(Cereals$sodium)
var(Cereals$fiber)
var(Cereals$carbo)
var(Cereals$sugars)
var(Cereals$potass)
var(Cereals$vitamins)
var(Cereals$shelf)
var(Cereals$weight)
var(Cereals$cups)
var(Cereals$rating)

# Skewness---
skewness(Cereals$calories)
skewness(Cereals$protein)
skewness(Cereals$fat)
skewness(Cereals$sodium)
skewness(Cereals$fiber)
skewness(Cereals$carbo)
skewness(Cereals$sugars)
skewness(Cereals$potass)
skewness(Cereals$vitamins)
skewness(Cereals$shelf)
skewness(Cereals$weight)
skewness(Cereals$cups)
skewness(Cereals$rating)

# Kurtosis---
kurtosis(Cereals$calories)
kurtosis(Cereals$protein)
kurtosis(Cereals$fat)
kurtosis(Cereals$sodium)
kurtosis(Cereals$fiber)
kurtosis(Cereals$carbo)
kurtosis(Cereals$sugars)
kurtosis(Cereals$potass)
kurtosis(Cereals$vitamins)
kurtosis(Cereals$shelf)
kurtosis(Cereals$weight)
kurtosis(Cereals$cups)
kurtosis(Cereals$rating)
```
# To get Percentages of values(n) in Rows and Columns---
```{r}
# For this purpose--Only select columns having Numeric values
Cereals[, 4:16]
# Or---
cereal_val<-select(Cereals,calories:rating) # to select only the numeric values from the given aforesaid dataset
cereal_val

# Conversion of a Dataframe containing Numeric values to a Matrix---
# cereal_val<-as.matrix(cereal_val)  
# cereal_val

# is.matrix(cereal_val) # To check/verify whether it is a Matrix or not

# Conversion of a Data-frame to a Matrix is important especially if one wants to derive row and and column values in Percentages for the given values----

library("rockchalk")
# Syntax: pctable(y ~ x, data = dat)
tab<-pctable(calories~mfr,data=Cereals)
summary(tab, rowpct = TRUE, colpct = FALSE)

tab<-pctable(calories~type,data=Cereals)
summary(tab, rowpct = TRUE, colpct = FALSE)

tab<-pctable(calories~protein,data=Cereals)
summary(tab, rowpct = TRUE, colpct = FALSE)

tab<-pctable(calories~fat,data=Cereals)
summary(tab, rowpct = TRUE, colpct = FALSE)

tab<-pctable(calories~sodium,data=Cereals)
summary(tab, rowpct = TRUE, colpct = FALSE)

tab<-pctable(calories~fiber,data=Cereals)
summary(tab, rowpct = TRUE, colpct = FALSE)

tab<-pctable(calories~carbo,data=Cereals)
summary(tab, rowpct = TRUE, colpct = FALSE)

tab<-pctable(calories~sugars,data=Cereals)
summary(tab, rowpct = TRUE, colpct = FALSE)

tab<-pctable(calories~potass,data=Cereals)
summary(tab, rowpct = TRUE, colpct = FALSE)

tab<-pctable(calories~vitamins,data=Cereals)
summary(tab, rowpct = TRUE, colpct = FALSE)

tab<-pctable(calories~shelf,data=Cereals)
summary(tab, rowpct = TRUE, colpct = FALSE)

tab<-pctable(calories~weight,data=Cereals)
summary(tab, rowpct = TRUE, colpct = FALSE)

tab<-pctable(calories~cups,data=Cereals)
summary(tab, rowpct = TRUE, colpct = FALSE)

tab<-pctable(calories~rating,data=Cereals)
summary(tab, rowpct = TRUE, colpct = FALSE)

```
# Cross-tabulations---
```{r}
# 2-Way Cross Tabulation
# The CrossTable( ) function in the gmodels package produces crosstabulations 
# modeled after PROC FREQ in SAS or Crosstabs in SPSS.
# # # ---Syntax:       CrossTable(mydata$myrowvar, mydata$mycolvar)--- # # # 
library(gmodels)

CrossTable(Cereals$name, Cereals$type)
CrossTable(Cereals$mfr, Cereals$type)
```
# Feature Engineering---
```{r}
# To classify Calories into 3 different Categories---
attach(Cereals)
Cereals$calorie_group[calories > 121] <- "High Calories"
Cereals$calorie_group[calories > 81 & calories <= 120] <- "Moderate Calories"
Cereals$calorie_group[calories <= 80] <- "Low Calories"
detach(Cereals)
View(Cereals)

# To change the order of the columns in a dataframe---
names(Cereals)
Cereals<-Cereals[,c(1:4,17,5:16)]
View(Cereals)


# To classify Sugar content in Cereal Products into 3 different Categories---

summary(Cereals$sugars)

attach(Cereals)
Cereals$sugar_group[sugars > 8] <- "High Sugar Content"
Cereals$sugar_group[sugars >= 6 & sugars <= 8] <- "Moderate Sugar Content"
Cereals$sugar_group[sugars < 6] <- "Low Sugar Content"
detach(Cereals)
View(Cereals)

# To change the order of the columns in a dataframe---
names(Cereals)
Cereals<-Cereals[,c(1:11,18,12:17)]
View(Cereals)


# To classify Customer Rating into 3 different Categories---
attach(Cereals)
Cereals$classified_rating[rating > 70] <- "High Rating"
Cereals$classified_rating[rating > 45 & calories<= 70] <- "Moderate Rating"
Cereals$classified_rating[rating <= 45] <- "Low Rating"
detach(Cereals)
View(Cereals)

# To drop Columns from the Dataframe---

# Syntax: 
# df = subset(mydata, select = -c(x,z))
# OR---
# drop <- c("x","z")
# df = mydata[,!(names(mydata) %in% c("x","z"))] 
# Or---
# drop <- c("x","z")
# df = mydata[,!(names(mydata) %in% drop)]

Cereals=subset(Cereals,select=-c(5,12))
View(Cereals)

# To delete/drop a column using dplyr package---
# Syntax:
# mydata2 = select(mydata, -a, -x, -y)

library(dplyr)
names(Cereals)
Cereals<-select(Cereals, -17)
View(Cereals)
```
# Correlations using Pearsons' Correlation (Parametric test), Kendall and Spearman's Correlation Coefficient Method (Non-Parametric test)---
```{r}
# A] Spearman's Correlation Coefficient Test (Non-Parametric test)---
cor.test(Cereals$calories,Cereals$protein, method="spearman")
cor.test(Cereals$calories,Cereals$fat, method="spearman")
cor.test(Cereals$calories,Cereals$sodium, method="spearman")
cor.test(Cereals$calories,Cereals$fiber, method="spearman")
cor.test(Cereals$calories,Cereals$carbo, method="spearman")
cor.test(Cereals$calories,Cereals$sugars, method="spearman")
cor.test(Cereals$calories,Cereals$potass, method="spearman")
cor.test(Cereals$calories,Cereals$vitamins, method="spearman")
cor.test(Cereals$calories,Cereals$shelf, method="spearman")
cor.test(Cereals$calories,Cereals$weight, method="spearman")
cor.test(Cereals$calories,Cereals$cups, method="spearman")
cor.test(Cereals$calories,Cereals$rating, method="spearman")

# B] Kendall method (Non-Parametric test)---
cor.test(Cereals$calories,Cereals$protein, method="kendall")
cor.test(Cereals$calories,Cereals$fat, method="kendall")
cor.test(Cereals$calories,Cereals$sodium, method="kendall")
cor.test(Cereals$calories,Cereals$fiber, method="kendall")
cor.test(Cereals$calories,Cereals$carbo, method="kendall")
cor.test(Cereals$calories,Cereals$sugars, method="kendall")
cor.test(Cereals$calories,Cereals$potass, method="kendall")
cor.test(Cereals$calories,Cereals$vitamins, method="kendall")
cor.test(Cereals$calories,Cereals$shelf, method="kendall")
cor.test(Cereals$calories,Cereals$weight, method="kendall")
cor.test(Cereals$calories,Cereals$cups, method="kendall")
cor.test(Cereals$calories,Cereals$rating, method="kendall")

# OR ---
library(Kendall)
round(cor(cereal_val, method="kendall"),2) 

# C]Pearson's Correlation Co-efficient Test (Parametric Test) ---
library(corrplot)
col_numeric <- sapply(Cereals, is.numeric)
numericalVars <- Cereals[,col_numeric]
corrMat <- cor(numericalVars,method=c("pearson"))
corrMat<-(round(corrMat,2))
corrMat

# To find Covariance between the variables---

round(cov(corrMat, use="complete.obs"),2) 
```
# Correlograms---
```{r}
# Correlogram is used for generating Correlation Matrix.
# Corrplot() is used to plot the graph of Correlation Matrix

corrplot(corrMat, method="pie")
corrplot(corrMat, method="circle")
corrplot(corrMat, method="square")

corrplot(corrMat, method="color")
corrplot(corrMat, method="shade")
corrplot(corrMat, method="number")

corrplot.mixed(corrMat, tl.pos = "lt")
corrplot.mixed(corrMat, tl.pos = "lt", diag = "u")
corrplot.mixed(corrMat, tl.pos = "lt", diag = "l")
corrplot.mixed(corrMat, tl.pos = "n")

# Positive correlations are displayed in blue and negative correlations in 
# red color. Color intensity and the size of the circle are proportional to 
# the correlation coefficients.

# Reordering the correlation matrix---
# correlogram with hclust reordering
corrplot(corrMat, order="hclust")

# Combining correlogram with the significance test &
# Computing the p-value of correlations

# To compute the matrix of p-value, a custom R function is used where--- :

# mat : is a matrix of data
# ... : further arguments to pass to the native R cor.test function
cor.mtest <- function(mat, ...) {
  mat <- as.matrix(mat)
  n <- ncol(mat)
  p.mat<- matrix(NA, n, n)
  diag(p.mat) <- 0
  for (i in 1:(n - 1)) {
    for (j in (i + 1):n) {
      tmp <- cor.test(mat[, i], mat[, j], ...)
      p.mat[i, j] <- p.mat[j, i] <- tmp$p.value
    }
  }
  colnames(p.mat) <- rownames(p.mat) <- colnames(mat)
  p.mat
}

# matrix of the p-value of the correlation
p.mat <- round(cor.mtest(corrMat),2)
p.mat
head(p.mat[, 1:13])


# To Add significance level to the correlogram
# Or to Strike-Off Insignificant Values # according to the significance # level---------

corrplot(corrMat, type="full", order="hclust", 
         p.mat = p.mat, sig.level = 0.01)

# OR----
# To Leave blank on no significant coefficient
corrplot(corrMat, type="full", order="hclust", 
         p.mat = p.mat, sig.level = 0.01, insig = "blank")


# To Customize the correlogram ----------------------

col <- colorRampPalette(c("#BB4444", "#EE9988", "#FFFFFF", "#77AADD", "#4477AA"))
corrplot(corrMat, method="color", col=col(200),  
         type="full", order="hclust", 
         addCoef.col = "black", # Add coefficient of correlation
         tl.col="maroon", tl.srt=45, #Text label color and rotation
         # Combine with significance
         p.mat = p.mat, sig.level = 0.01, insig = "blank", 
         # hide correlation coefficient on the principal diagonal
         diag=FALSE)

# OR---
col <- colorRampPalette(c("#7F0000", "red", "#FF7F00", "yellow", "white",
                           "cyan", "#007FFF", "blue", "#00007F"))
corrplot(corrMat, method="color", col=col(200),  
         type="full", order="hclust", 
         addCoef.col = "black", # Add coefficient of correlation
         tl.col="maroon", tl.srt=45, #Text label color and rotation
         # Combine with significance
         p.mat = p.mat, sig.level = 0.01, insig = "blank", 
         # hide correlation coefficient on the principal diagonal
         diag=FALSE)

# OR---

col <- colorRampPalette(c("#67001F", "#B2182B", "#D6604D", "#F4A582",
                           "#FDDBC7", "#FFFFFF", "#D1E5F0", "#92C5DE",
                           "#4393C3", "#2166AC", "#053061"))
corrplot(corrMat, method="color", col=col(200),  
         type="full", order="hclust", 
         addCoef.col = "black", # Add coefficient of correlation
         tl.col="maroon", tl.srt=45, #Text label color and rotation
         # Combine with significance
         p.mat = p.mat, sig.level = 0.01, insig = "blank", 
         # hide correlation coefficient on the principal diagonal
         diag=FALSE)

# OR---

col <- colorRampPalette(c("red", "white", "blue")) 
corrplot(corrMat, method="color", col=col(200),  
         type="full", order="hclust", 
         addCoef.col = "black", # Add coefficient of correlation
         tl.col="maroon", tl.srt=45, #Text label color and rotation
         # Combine with significance
         p.mat = p.mat, sig.level = 0.01, insig = "blank", 
         # hide correlation coefficient on the principal diagonal
         diag=FALSE)


# Thus the correlation of variables within the given sampling dataset  has 
# been checked for and noted. 

corrplot(corrMat, order = "AOE")
corrplot(corrMat, order = "FPC")
corrplot(corrMat, order = "alphabet")
corrplot(corrMat, order = "hclust", addrect = 2)
corrplot(corrMat, order = "hclust", addrect = 3,method= "number")
corrplot(corrMat, order = "hclust", addrect = 3)
```
# Bar-plots---
```{r}
barplot(Cereals$calories, beside = TRUE, angle = 15+10*1:5, density=60,
        col = c("lightblue", "mistyrose", "lightcyan",
                "lavender", "cornsilk"),border = "brown",
        legend = rownames(Cereals$calories), ylim = c(50, 160))
title(main = "Calories content in the Cereals", font.main=4)

barplot(Cereals$protein, beside = TRUE, angle = 15+10*1:5, density=60,
        col = c("lightblue", "mistyrose", "lightcyan",
                "lavender", "cornsilk"),border = "dark blue",
        legend = rownames(Cereals$protein), ylim = c(1,6))
title(main = "Protein content in the Cereals", font.main=4)

barplot(Cereals$fat, beside = TRUE, angle = 15+10*1:5, density=60,
        col = c("lightblue", "mistyrose", "lightcyan",
                "lavender", "cornsilk"),border = "black",
        legend = rownames(Cereals$fat), ylim = c(1,4))
title(main = "Fat content in the Cereals", font.main=4)

barplot(Cereals$sodium, beside = TRUE, angle = 15+10*1:5, density=60,
        col = c("lightblue", "mistyrose", "lightcyan",
                "lavender", "cornsilk"),border = "red",
        legend = rownames(Cereals$sodium), ylim = c(0,290))
title(main = "Sodium content in the Cereals", font.main=4)

barplot(Cereals$fiber, beside = TRUE, angle = 15+10*1:5, density=60,
        col = c("lightblue", "mistyrose", "lightcyan",
                "lavender", "cornsilk"),border = "purple",
        legend = rownames(Cereals$fiber), ylim = c(0,9))
title(main = "Fibre content in the Cereals", font.main=4)

barplot(Cereals$carbo, beside = TRUE, angle = 15+10*1:5, density=60,
        col = c("lightblue", "mistyrose", "lightcyan",
                "lavender", "cornsilk"),border = "orange",
        legend = rownames(Cereals$carbo), ylim = c(9,23))
title(main = "Carbohydrate content in the Cereals", font.main=4)

barplot(Cereals$sugars, beside = TRUE, angle = 15+10*1:5, density=60,
        col = c("lightblue", "mistyrose", "lightcyan",
                "lavender", "cornsilk"),border = "lavender",
        legend = rownames(Cereals$sugars), ylim = c(0,15))
title(main = "Sugar content in the Cereals", font.main=4)

barplot(Cereals$potass, beside = TRUE, angle = 15+10*1:5, density=60,
        col = c("lightblue", "mistyrose", "lightcyan",
                "lavender", "cornsilk"),border = "violet",
        legend = rownames(Cereals$potass), ylim = c(25,280))
title(main = "Potassium content in the Cereals", font.main=4)

barplot(Cereals$vitamins, beside = TRUE, angle = 15+10*1:5, density=60,
        col = c("lightblue", "mistyrose", "lightcyan",
                "lavender", "cornsilk"),border = "aquamarine",
        legend = rownames(Cereals$vitamins), ylim = c(0,60))
title(main = "Vitamins content in the Cereals", font.main=4)

barplot(Cereals$shelf, beside = TRUE, angle = 15+10*1:5, density=60,
        col = c("lightblue", "mistyrose", "lightcyan",
                "lavender", "cornsilk"),border = "yellow",
        legend = rownames(Cereals$shelf), ylim = c(1,3))
title(main = " Shelf placement of the Breakfast Cereals", font.main=4)

barplot(Cereals$weight, beside = TRUE, angle = 15+10*1:5, density=60,
        col = c("lightblue", "mistyrose", "lightcyan",
                "lavender", "cornsilk"),border = "peachpuff",
        legend = rownames(Cereals$weight), ylim = c(1,2))
title(main = "Cereals - Packaging Weight", font.main=4)

barplot(Cereals$cups, beside = TRUE, angle = 15+10*1:5, density=60,
        col = c("lightblue", "mistyrose", "lightcyan",
                "lavender", "cornsilk"),border = "tan",
        legend = rownames(Cereals$cups), ylim = c(0,2))
title(main = "Measurement - Cups per serving", font.main=4)

barplot(Cereals$rating, beside = TRUE, angle = 15+10*1:5, density=60,
        col = c("lightblue", "mistyrose", "lightcyan",
                "lavender", "cornsilk"),border = "yellow",
        legend = rownames(Cereals$rating), ylim = c(18,94))
title(main = "Cereals - Customer Rating Index", font.main=4)
```
# Pie-Charts---
# Useful for Frequency of factors---
```{r}
pie(table(Cereals$mfr))
pie(table(Cereals$type))
pie(table(Cereals$calories))
pie(table(Cereals$protein))
pie(table(Cereals$fat))
pie(table(Cereals$sugars))
pie(table(Cereals$fiber))
pie(table(Cereals$vitamins))
pie(table(Cereals$shelf))
pie(table(Cereals$weight))
pie(table(Cereals$cups))
```
# Histograms---
```{r}
par(mfrow=c(1, 1))

# To plot the Histogram-----

hist(Cereals,probability=T,  main="Histogram of Cereals dataset")

plotNormalHistogram(corrMat)

hist(Cereals$calories, probability = T, main="Histogram - Cereals - Calories 
     # Content")
hist(Cereals$protein, col='purple', xlab="proteins", main="Histogram - Cereals
     # - Protein Content")
hist(Cereals$fat, col='tan', main="Histogram - Cereals - Fat Content")
hist(Cereals$sodium, col='violet', main="Histogram - Cereals - Sodium
     # Content")
hist(Cereals$fiber,col='beige', main="Histogram - Cereals - Fiber Content")
hist(Cereals$carbo,col='coral', main="Histogram - Cereals - Carbohydrates
     # Content")
hist(Cereals$sugars, col='khaki', main="Histogram - Cereals - Sugar Content")
hist(Cereals$potass, col='magenta',main="Histogram - Cereals - Potassium
     # Content")
hist(Cereals$vitamins, col='aquamarine', main="Histogram - Cereals - Vitamins
     # Content")
hist(Cereals$shelf, col='light green', main="Histogram - Cereals - Shelf
     # Depiction")
hist(Cereals$weight,col='sky blue', main="Histogram - Cereals - Product
     # Weightage")
hist(Cereals$cups, col='orange', main="Histogram - Cereals - Cups for
     # Consumption")
hist(Cereals$rating, col='chocolate', main="Histogram - Cereals - Rating")


# Histogram for 1 way data---

histogram(~ calories | type,
          data=Cereals,
          layout=c(1,2))      #  columns and rows of individual plots

histogram(~ calories | mfr,
          data=Cereals,
          layout=c(1,1))      #  columns and rows of individual plots

histogram(~ calories | calories,
          data=Cereals,
          layout=c(1,5))

histogram(~ calories | protein,
          data=Cereals,
          layout=c(1,3))

histogram(~ calories | fat,
          data=Cereals,
          layout=c(1,3))

histogram(~ calories | vitamins,
          data=Cereals,
          layout=c(1,3))

histogram(~ calories | fiber,
          data=Cereals,
          layout=c(1,3))

histogram(~ calories | sugars,
          data=Cereals,
          layout=c(1,4))


library(devtools)
install_github("easyGgplot2", "kassambara")
library(easyGgplot2)

calories_content=Cereals$calories
plotNormalHistogram(calories_content, col='yellow')

protein_content=Cereals$protein
plotNormalHistogram(protein_content, col='ivory')

fat_content=Cereals$fat
plotNormalHistogram(fat_content,col='dark green')

sodium_content=Cereals$sodium
plotNormalHistogram(sodium_content,col='aquamarine')

fiber_Content=Cereals$fiber
plotNormalHistogram(fiber_Content, col='orange')

carbo_content=Cereals$carbo
plotNormalHistogram(carbo_content, col='grey')

sugars_content=Cereals$sugars
plotNormalHistogram(sugars_content, col='sea green')

potass_content=Cereals$potass
plotNormalHistogram(potass_content, col='maroon')

vitamins_content=Cereals$vitamins
plotNormalHistogram(vitamins_content, col='bisque')

shelf_placement=Cereals$shelf
plotNormalHistogram(shelf_placement, col='tan')

package_weight=Cereals$weight
plotNormalHistogram(package_weight, col='turquoise')

serving_size_in_cups=Cereals$cups
plotNormalHistogram(serving_size_in_cups, col='peachpuff')

customer_rating=Cereals$rating
plotNormalHistogram(customer_rating, col='slategray2')
```
# Stem and Leaf Plots---
```{r}
stem(log(Cereals$calories))
stem(log(Cereals$protein))
stem(log(Cereals$fat))
stem(log(Cereals$sodium))
stem(log(Cereals$fiber))
stem(log(Cereals$carbo))
stem(log(Cereals$sugars))
stem(log(Cereals$potass))
stem(log(Cereals$vitamins))
stem(log(Cereals$shelf))
stem(log(Cereals$weight))
stem(log(Cereals$cups))
stem(log(Cereals$rating))
```
# Scatter Plots---
```{r}
# To generate Scatter Plots----
# Simple Scatterplot

plot(Cereals$protein, Cereals$calories, main="Scatter Plot", xlab="Proteins", ylab="Calories", pch="*", col="red", cex=2)
abline(lm(Cereals$calories ~ Cereals$protein, data=Cereals), col="blue", lwd=3, lty=2)
lines(lowess(Cereals$protein, Cereals$calories),col="dark green")

plot(Cereals$fat, Cereals$calories, main="Scatter Plot", xlab="Fat_Content", ylab="Calories", pch="*", col="red", cex=2)
abline(lm(Cereals$calories ~ Cereals$fat, data=Cereals), col="blue", lwd=3, lty=2)
lines(lowess(Cereals$fat, Cereals$calories),col="dark green")

plot(Cereals$sodium, Cereals$calories, main="Scatter Plot", xlab="Sodium_Content", ylab="Calories", pch="*", col="red", cex=2)
abline(lm(Cereals$calories ~ Cereals$sodium, data=Cereals), col="blue", lwd=3, lty=2)
lines(lowess(Cereals$sodium, Cereals$calories),col="dark green")

plot(Cereals$fiber, Cereals$calories, main="Scatter Plot", xlab="Fibre_Content", ylab="Calories", pch="*", col="red", cex=2)
abline(lm(Cereals$calories ~ Cereals$fiber, data=Cereals), col="blue", lwd=3, lty=2)
lines(lowess(Cereals$fiber, Cereals$calories),col="dark green")

plot(Cereals$fiber, Cereals$calories, main="Scatter Plot", xlab="Fibre_Content", ylab="Calories", pch="*", col="red", cex=2)
abline(lm(Cereals$calories ~ Cereals$fiber, data=Cereals), col="blue", lwd=3, lty=2)
lines(lowess(Cereals$fiber, Cereals$calories),col="dark green")

plot(Cereals$carbo, Cereals$calories, main="Scatter Plot", xlab="Carbohydrate_Content", ylab="Calories", pch="*", col="red", cex=2)
abline(lm(Cereals$calories ~ Cereals$carbo, data=Cereals), col="blue", lwd=3, lty=2)
lines(lowess(Cereals$carbo, Cereals$calories),col="dark green")

plot(Cereals$sugars, Cereals$calories, main="Scatter Plot", xlab="Sugar_Content", ylab="Calories", pch="*", col="red", cex=2)
abline(lm(Cereals$calories ~ Cereals$sugars, data=Cereals), col="blue", lwd=3, lty=2)
lines(lowess(Cereals$sugars, Cereals$calories),col="dark green")

plot(Cereals$potass, Cereals$calories, main="Scatter Plot", xlab="Potassium_Content", ylab="Calories", pch="*", col="red", cex=2)
abline(lm(Cereals$calories ~ Cereals$potass, data=Cereals), col="blue", lwd=3, lty=2)
lines(lowess(Cereals$potass, Cereals$calories),col="dark green")

plot(Cereals$vitamins, Cereals$calories, main="Scatter Plot", xlab="Vitamin_Content", ylab="Calories", pch="*", col="red", cex=2)
abline(lm(Cereals$calories ~ Cereals$vitamins, data=Cereals), col="blue", lwd=3, lty=2)
lines(lowess(Cereals$vitamins, Cereals$calories),col="dark green")

plot(Cereals$shelf, Cereals$calories, main="Scatter Plot", xlab="Shelf_Placement", ylab="Calories", pch="*", col="red", cex=2)
abline(lm(Cereals$calories ~ Cereals$shelf, data=Cereals), col="blue", lwd=3, lty=2)
lines(lowess(Cereals$shelf, Cereals$calories),col="dark green")

plot(Cereals$weight, Cereals$calories, main="Scatter Plot", xlab="Shelf_Placement", ylab="Calories", pch="*", col="red", cex=2)
abline(lm(Cereals$calories ~ Cereals$weight, data=Cereals), col="blue", lwd=3, lty=2)
lines(lowess(Cereals$weight, Cereals$calories),col="dark green")

plot(Cereals$cups, Cereals$calories, main="Scatter Plot", xlab="Serving Size (in cups)", ylab="Calories", pch="*", col="red", cex=2)
abline(lm(Cereals$calories ~ Cereals$cups, data=Cereals), col="blue", lwd=3, lty=2)
lines(lowess(Cereals$cups, Cereals$calories),col="dark green")

plot(Cereals$rating, Cereals$calories, main="Scatter Plot", xlab="Customer Rating Indices", ylab="Calories", pch="*", col="red", cex=2)
abline(lm(Cereals$calories ~ Cereals$rating, data=Cereals), col="blue", lwd=3, lty=2)
lines(lowess(Cereals$rating, Cereals$calories),col="dark green")


# Scatterplot Matrices---

# Basic Scatterplot Matrix
pairs(~calories+protein+fat+sodium +fiber+carbo+sugars+potass+vitamins,data=Cereals,
   main="Cereals - Nutritional_Content_Scatterplot_Matrix")

pairs(~calories+shelf+weight+cups+rating,data=Cereals,
   main="Simple Scatterplot Matrix")

```
# Box & Whisker Plots---
```{r}
boxplot(Cereals$calories~Cereals$mfr,notch=TRUE, 
        col=(c("gold","darkgreen")),
        main="Cereals_dataset", 
        xlab='Manufacturer',ylab='Calories')

boxplot(Cereals$calories~Cereals$type,notch=TRUE, 
        col=(c("gold","darkgreen")),
        main="Cereals_dataset", 
        xlab='Type of Breakfast Cereals',ylab='Calories')

boxplot(Cereals$calories~Cereals$protein,notch=TRUE, 
        col=(c("gold","darkgreen")),
        main="Cereals_dataset", 
        xlab='Protein',ylab='Calories')

boxplot(Cereals$calories~Cereals$fat,notch=TRUE, 
        col=(c("gold","darkgreen")),
        main="Cereals_dataset", 
        xlab='Fats',ylab='Calories')

boxplot(Cereals$calories~Cereals$sodium,notch=TRUE, 
        col=(c("gold","darkgreen")),
        main="Cereals_dataset", 
        xlab='Sodium',ylab='Calories')

boxplot(Cereals$calories~Cereals$fiber,notch=TRUE, 
        col=(c("gold","darkgreen")),
        main="Cereals_dataset", 
        xlab='Fiber',ylab='Calories')

boxplot(Cereals$calories~Cereals$carbo,notch=TRUE, 
        col=(c("gold","darkgreen")),
        main="Cereals_dataset", 
        xlab='Carbohydrates',ylab='Calories')

boxplot(Cereals$calories~Cereals$sugars,notch=TRUE, 
        col=(c("gold","darkgreen")),
        main="Cereals_dataset", 
        xlab='Sugar',ylab='Calories')

boxplot(Cereals$calories~Cereals$potass,notch=TRUE, 
        col=(c("gold","darkgreen")),
        main="Cereals_dataset", 
        xlab='Potassium',ylab='Calories')

boxplot(Cereals$calories~Cereals$vitamins,notch=TRUE, 
        col=(c("gold","darkgreen")),
        main="Cereals_dataset", 
        xlab='Vitamins',ylab='Calories')

boxplot(Cereals$calories~Cereals$shelf,notch=TRUE, 
        col=(c("gold","darkgreen")),
        main="Cereals_dataset", 
        xlab='Shelf',ylab='Calories')

boxplot(Cereals$calories~Cereals$weight,notch=TRUE, 
        col=(c("gold","darkgreen")),
        main="Cereals_dataset", 
        xlab='Weightage',ylab='Calories')

boxplot(Cereals$calories~Cereals$cups,notch=TRUE, 
        col=(c("gold","darkgreen")),
        main="Cereals_dataset",
        xlab='Cups per Serving',ylab='Calories')

boxplot(Cereals$calories~Cereals$rating,notch=FALSE, 
        col=(c("gold","darkgreen")),
        main="Cereals_dataset", 
        xlab='Customer Rating',ylab='Calories')
```
# Dot Plots---
```{r}
require(ggplot2)
library(ggplot2)
library(scales)

###
# Dot Plots---
ggplot(Cereals, aes(x=mfr, y=calories),) + 
  geom_point(col="tomato2", size=4) +   # Draw points
  geom_segment(aes(x=mfr, xend=mfr, 
                   y=min(calories), yend=max(calories)), 
                   linetype="dashed", size=0.1) +   # Draw dashed lines
labs(title="Dot Plot", subtitle="Calories content across Breakfast Cereals by different Manufacturers", caption = "source: Cereals_Dataset") 

ggplot(Cereals, aes(x=type, y=calories),) + 
  geom_point(col="tomato2", size=4) +   # Draw points
  geom_segment(aes(x=type, xend=type, 
                   y=min(calories), yend=max(calories)), 
                   linetype="dashed", size=0.1) +   # Draw dashed lines
labs(title="Dot Plot", subtitle="Calories content versus Cereal Types",       
     caption = "source: Cereals_Dataset") 

ggplot(Cereals, aes(x=protein, y=calories),) + 
  geom_point(col="tomato2", size=4) +   # Draw points
  geom_segment(aes(x=protein, xend=protein, 
                   y=min(calories), yend=max(calories)), 
                   linetype="dashed", size=0.1) +   # Draw dashed lines
labs(title="Dot Plot", subtitle="Cereals - Proteins and corresponding Calories
     Content", caption = "source: Cereals_Dataset")

ggplot(Cereals, aes(x=fat, y=calories),) + 
  geom_point(col="tomato2", size=4) +   # Draw points
  geom_segment(aes(x=fat, xend=fat, 
                   y=min(calories), yend=max(calories)), 
                   linetype="dashed", size=0.1) +   # Draw dashed lines
labs(title="Dot Plot", subtitle="Cereals - Fats and corresponding Calories
     Content", caption = "source: Cereals_Dataset")

ggplot(Cereals, aes(x=sodium, y=calories),) + 
  geom_point(col="tomato2", size=4) +   # Draw points
  geom_segment(aes(x=sodium, xend=sodium, 
                   y=min(calories), yend=max(calories)), 
                   linetype="dashed", size=0.1) +   # Draw dashed lines
labs(title="Dot Plot", subtitle="Cereals - Sodium and corresponding Calories
     Content", caption = "source: Cereals_Dataset")

ggplot(Cereals, aes(x=fiber, y=calories),) + 
  geom_point(col="tomato2", size=4) +   # Draw points
  geom_segment(aes(x=fiber, xend=fiber, 
                   y=min(calories), yend=max(calories)), 
                   linetype="dashed", size=0.1) +   # Draw dashed lines
labs(title="Dot Plot", subtitle="Cereals - Fibre and corresponding Calories
     Content", caption = "source: Cereals_Dataset")

ggplot(Cereals, aes(x=carbo, y=calories),) + 
  geom_point(col="tomato2", size=4) +   # Draw points
  geom_segment(aes(x=carbo, xend=carbo, 
                   y=min(calories), yend=max(calories)), 
                   linetype="dashed", size=0.1) +   # Draw dashed lines
labs(title="Dot Plot", subtitle="Cereals - Carbohydrates and corresponding
     Calories Content", caption = "source: Cereals_Dataset")


ggplot(Cereals, aes(x=sugars, y=calories),) + 
  geom_point(col="tomato2", size=4) +   # Draw points
  geom_segment(aes(x=sugars, xend=sugars, 
                   y=min(calories), yend=max(calories)), 
                   linetype="dashed", size=0.1) +   # Draw dashed lines
labs(title="Dot Plot", subtitle="Cereals - Sugar and corresponding Calories
     Content", caption = "source: Cereals_Dataset")

ggplot(Cereals, aes(x=potass, y=calories),) + 
  geom_point(col="tomato2", size=4) +   # Draw points
  geom_segment(aes(x=potass, xend=potass, 
                   y=min(calories), yend=max(calories)), 
                   linetype="dashed", size=0.1) +   # Draw dashed lines
labs(title="Dot Plot", subtitle="Cereals - Potassium and corresponding
     Calories Content", caption = "source: Cereals_Dataset")

ggplot(Cereals, aes(x=vitamins, y=calories),) + 
  geom_point(col="tomato2", size=4) +   # Draw points
  geom_segment(aes(x=vitamins, xend=vitamins, 
                   y=min(calories), yend=max(calories)), 
                   linetype="dashed", size=0.1) +   # Draw dashed lines
labs(title="Dot Plot", subtitle="Cereals - Vitamins and corresponding
     Calories Content", caption = "source: Cereals_Dataset")

ggplot(Cereals, aes(x=shelf, y=calories),) + 
  geom_point(col="tomato2", size=4) +   # Draw points
  geom_segment(aes(x=shelf, xend=shelf, 
                   y=min(calories), yend=max(calories)), 
                   linetype="dashed", size=0.1) +   # Draw dashed lines
labs(title="Dot Plot", subtitle="Cereals - Positioning and Floor Placement",
     caption = "source: Cereals_Dataset")

ggplot(Cereals, aes(x=weight, y=calories),) + 
  geom_point(col="tomato2", size=4) +   # Draw points
  geom_segment(aes(x=weight, xend=weight, 
                   y=min(calories), yend=max(calories)), 
                   linetype="dashed", size=0.1) +   # Draw dashed lines
labs(title="Dot Plot", subtitle="Breakfast Cereal Products - Weightage of the
     Package", caption = "source: Cereals_Dataset")

ggplot(Cereals, aes(x=cups, y=calories),) + 
  geom_point(col="tomato2", size=4) +   # Draw points
  geom_segment(aes(x=cups, xend=cups, 
                   y=min(calories), yend=max(calories)), 
                   linetype="dashed", size=0.1) +   # Draw dashed lines
labs(title="Dot Plot", subtitle="Breakfast Cereal Products - Measurement- Cups
     per Serving", caption = "source: Cereals_Dataset")

ggplot(Cereals, aes(x=rating, y=calories),) + 
  geom_point(col="tomato2", size=4) +   # Draw points
  geom_segment(aes(x=rating, xend=rating, 
                   y=min(calories), yend=max(calories)), 
                   linetype="dashed", size=0.1) +   # Draw dashed lines
labs(title="Dot Plot", subtitle="A Glance - Customer Rating Indices of
     Breakfast Cereal Products", caption = "source: Cereals_Dataset")

# Dot plot with mean point---
library(devtools)
library(ggplot2)
install_github("easyGgplot2", "kassambara")
library(easyGgplot2)

ggplot2.dotplot(data=Cereals, xName='protein',yName='calories',
                addMean=TRUE, meanPointShape=23, meanPointSize=4,
                meanPointColor="dark green", meanPointFill="red",
                backgroundColor="bisque2", gridColor="white")

ggplot2.dotplot(data=Cereals, xName='fat',yName='calories',
                addMean=TRUE, meanPointShape=23, meanPointSize=4,
                meanPointColor="dark green", meanPointFill="red",
                backgroundColor="yellow", gridColor="white")

ggplot2.dotplot(data=Cereals, xName='sodium',yName='calories',
                addMean=TRUE, meanPointShape=23, meanPointSize=4,
                meanPointColor="dark green", meanPointFill="red",
                backgroundColor="orange", gridColor="white")

ggplot2.dotplot(data=Cereals, xName='fiber',yName='calories',
                addMean=TRUE, meanPointShape=23, meanPointSize=4,
                meanPointColor="dark green", meanPointFill="red",
                backgroundColor="light coral", gridColor="white")

ggplot2.dotplot(data=Cereals, xName='carbo',yName='calories',
                addMean=TRUE, meanPointShape=23, meanPointSize=4,
                meanPointColor="dark green", meanPointFill="red",
                backgroundColor="peachpuff", gridColor="white")

ggplot2.dotplot(data=Cereals, xName='sugars',yName='calories',
                addMean=TRUE, meanPointShape=23, meanPointSize=4,
                meanPointColor="dark green", meanPointFill="red",
                backgroundColor="light blue", gridColor="white")

ggplot2.dotplot(data=Cereals, xName='potass',yName='calories',
                addMean=TRUE, meanPointShape=23, meanPointSize=4,
                meanPointColor="dark green", meanPointFill="red",
                backgroundColor="light green", gridColor="white")

ggplot2.dotplot(data=Cereals, xName='vitamins',yName='calories',
                addMean=TRUE, meanPointShape=23, meanPointSize=4,
                meanPointColor="dark green", meanPointFill="red",
                backgroundColor="aquamarine", gridColor="white")

ggplot2.dotplot(data=Cereals, xName='shelf',yName='calories',
                addMean=TRUE, meanPointShape=23, meanPointSize=4,
                meanPointColor="dark green", meanPointFill="red",
                backgroundColor="sky blue", gridColor="white")

ggplot2.dotplot(data=Cereals, xName='weight',yName='calories',
                addMean=TRUE, meanPointShape=23, meanPointSize=4,
                meanPointColor="dark green", meanPointFill="red",
                backgroundColor="sea green", gridColor="white")

ggplot2.dotplot(data=Cereals, xName='cups',yName='calories',
                addMean=TRUE, meanPointShape=23, meanPointSize=4,
                meanPointColor="dark green", meanPointFill="red",
                backgroundColor="pink", gridColor="white")

ggplot2.dotplot(data=Cereals, xName='rating',yName='calories',
                addMean=TRUE, meanPointShape=23, meanPointSize=4,
                meanPointColor="dark green", meanPointFill="red",
                backgroundColor="lavender", gridColor="white")


```
# ggplots---
```{r}
ggplot(Cereals, aes(x = mfr, y = calories)) +  geom_point()
ggplot(Cereals, aes(x = type, y = calories)) +  geom_point()
ggplot(Cereals, aes(x = protein, y = calories)) +  geom_point()
ggplot(Cereals, aes(x = fat, y = calories)) +  geom_point()
ggplot(Cereals, aes(x = sodium, y = calories)) +  geom_point()
ggplot(Cereals, aes(x = fiber, y = calories)) +  geom_point()
ggplot(Cereals, aes(x = carbo, y = calories)) +  geom_point()
ggplot(Cereals, aes(x = sugars, y = calories)) +  geom_point()
ggplot(Cereals, aes(x = potass, y = calories)) +  geom_point()
ggplot(Cereals, aes(x = vitamins, y = calories)) +  geom_point()
ggplot(Cereals, aes(x = shelf, y = calories)) +  geom_point()
ggplot(Cereals, aes(x = weight, y = calories)) +  geom_point()
ggplot(Cereals, aes(x = cups, y = calories)) +  geom_point()
ggplot(Cereals, aes(x = rating, y = calories)) +  geom_point()

```
# qq plots (Quantile-Quantile Plots) or Normality Plots---
```{r}
library(car)
qqPlot(Cereals$calories,main='QQ Plot of Calories in Breakfast Cereals', col="purple")
qqPlot(Cereals$protein,main='QQ Plot of Proteins in Breakast Cereals', col="purple")
qqPlot(Cereals$fat,main='QQ Plot of Fats in Breakast Cereals', col="purple")
qqPlot(Cereals$sodium,main='QQ Plot of Sodium in Breakast Cereals', col="purple")
qqPlot(Cereals$fiber,main='QQ Plot of Fibre in Breakast Cereals', col="purple")
qqPlot(Cereals$carbo,main='QQ Plot of Carbohydrates in Breakast Cereals', col="purple")
qqPlot(Cereals$sugars,main='QQ Plot of Sugars in Breakast Cereals', col="purple")
qqPlot(Cereals$potass,main='QQ Plot of Potassium in Breakast Cereals', col="purple")
qqPlot(Cereals$vitamins,main='QQ Plot of Vitamins in Breakast Cereals', col="purple")
qqPlot(Cereals$shelf,main='QQ Plot of Breakast Cereals Floor Placement', col="purple")
qqPlot(Cereals$weight,main='QQ Plot of Breakast Cereals Packaged Weights', col="purple")
qqPlot(Cereals$cups,main='QQ Plot of Cups per serving of Breakast Cereals', col="purple")
qqPlot(Cereals$rating,main='QQ Plot of Breakast Cereals Rating by Customers', col="purple")

qqnorm(corrMat, main="QQ Plot")
qqline(corrMat)

```
# ggqq Plot---
```{r}
ggqqplot(Cereals$calories, color="yellow",palette = NULL)
ggqqplot(Cereals$protein, color="tan",palette = NULL)
ggqqplot(Cereals$fat, color="turquoise",palette = NULL)
ggqqplot(Cereals$sodium, color="sky blue",palette = NULL)
ggqqplot(Cereals$fiber, color="light green",palette = NULL)
ggqqplot(Cereals$carbo, color="dark green",palette = NULL)
ggqqplot(Cereals$sugars, color="orange",palette = NULL)
ggqqplot(Cereals$potass, color="lavender",palette = NULL)
ggqqplot(Cereals$vitamins, color="bisque3",palette = NULL)
ggqqplot(Cereals$shelf, color="brown",palette = NULL)
ggqqplot(Cereals$weight, color="sea green",palette = NULL)
ggqqplot(Cereals$cups, color="aquamarine",palette = NULL)
ggqqplot(Cereals$rating, color="coral",palette = NULL)

```
# Density Plots-
```{r}
# Filled Density Plot
d <- density(Cereals$calories)
plot(d, main="Breakfast Cereals - Calories")
polygon(d, col="red", border="blue")

d <- density(Cereals$protein)
plot(d, main="Breakfast Cereals - Proteins")
polygon(d, col="purple", border="blue")

d <- density(Cereals$fat)
plot(d, main="Breakfast Cereals - Fats")
polygon(d, col="yellow", border="blue")

d <- density(Cereals$sodium)
plot(d, main="Breakfast Cereals - Sodium")
polygon(d, col="violet", border="blue")

d <- density(Cereals$fiber)
plot(d, main="Breakfast Cereals - Fiber")
polygon(d, col="sea green", border="blue")

d <- density(Cereals$fiber)
plot(d, main="Breakfast Cereals - Fiber")
polygon(d, col="sea green", border="blue")

d <- density(Cereals$carbo)
plot(d, main="Breakfast Cereals - Carbohydrates")
polygon(d, col="aquamarine", border="blue")

d <- density(Cereals$sugars)
plot(d, main="Breakfast Cereals - Sugar")
polygon(d, col="coral", border="blue")

d <- density(Cereals$potass)
plot(d, main="Breakfast Cereals - Potassium")
polygon(d, col="tan", border="blue")

d <- density(Cereals$vitamins)
plot(d, main="Breakfast Cereals - Vitamins")
polygon(d, col="dark green", border="blue")

d <- density(Cereals$shelf)
plot(d, main="Breakfast Cereals - floor placement")
polygon(d, col="pink", border="blue")

d <- density(Cereals$weight)
plot(d, main="Breakfast Cereals - Packaged Weights")
polygon(d, col="brown", border="blue")

d <- density(Cereals$cups)
plot(d, main="Breakfast Cereals - Cups per sering")
polygon(d, col="dark blue", border="blue")

d <- density(Cereals$rating)
plot(d, main="Breakfast Cereals - Customer Rating Indices")
polygon(d, col="light green", border="blue")

```
